R-LIME\@: Rectangular Constraints and Optimization for Local Interpretable Model-agnostic Explanation Methods

### 2024-08-15 paper.tex
feat: remove all submodules for camera-ready

\usepackage[export]{adjustbox} % for valign option in \includegraphics
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amssymb} % for \mathbb
\usepackage{array} % for m column type
\usepackage{bbm} % for \mathbbm
\usepackage{booktabs} % for \toprule, \midrule, \bottomrule
\usepackage{cleveref} % for \cref
\usepackage{color,soul} % for \hl
\usepackage{csvsimple} % for \csvreader
\usepackage[T1]{fontenc} % for T1 font encoding
\usepackage{graphicx} % for \includegraphics
\usepackage{pgffor} % for \foreach
\usepackage[labelformat=simple]{subcaption} % for subfigure environment
\usepackage{tikz}
\usetikzlibrary{positioning}

@@

\begin{document}
\begin{center}
  % smaller title font only for rebuttal
  % additional two empty lines at the end of the title
  \vspace*{-22pt}
  \begin{tabular}[t]{c}{
      \large\bf
      Paper ID \paperID{}
    }
  \end{tabular}
  \par
  % additional small space at the end of the author name
  % additional empty line at the end of the title block
\end{center}
We deeply appreciate all the reviewers who made sharp and valuable comments
on our paper and gave us the opportunity to submit a revised version.
We have done our best for the revision according to their comments as shown below.
We also thank in advance all the reviewers for reconsidering
our revised paper's suitability for the conference.

\section*{Summary of revisions}
We appreciate all the reviewers for their clear and insightful
comments.
We have improved our paper based on their comments.
The major revision points are listed as follows:
\begin{itemize}
  \item We mentioned the names of other existing methods in \cref{sec:related-work}.
  \item We added discussion about parameter selection in \cref{sec:param}.
  \item We conducted qualitative and quantitative comparisons
        between Anchor and R-LIME in \cref{sec:exp-qual,sec:exp-anchor}.
  \item We renamed the section `Challenges and Future Work' to `Discussion'.
\end{itemize}
Please see below for a point-by-point response to each reviewer's comments.

\newenvironment{mycomment}{
  \vspace{10pt}\hspace{.02\textwidth}\begin{minipage}{.92\textwidth}
    }{\end{minipage}}

\section*{Responding to Reviewer \#1}
Suggestions for Rebuttal:
\begin{enumerate}
  \setlength{\itemsep}{15pt}
  \item Offer guidance on how to select optimal parameters for different
        datasets and models.

        \begin{mycomment}
          We appreciate your suggestion.
          We added \cref{sec:param} to provide guidance on
          how parameters should be selected in practice.
        \end{mycomment}

  \item Include a discussion of other model-agnostic interpretability methods,
        such as SHAP, to provide a more comprehensive overview.

        \begin{mycomment}
          Thank you for your valuable suggestion.
          Although we acknowledge the importance of including an overview of
          other model-agnostic interpretability methods,
          due to space constraints, we only mentioned the names of some
          other methods in \cref{sec:related-work}.
        \end{mycomment}

  \item Add experimental comparisons with more other model-agnostic \\
        interpretability methods to better evaluate R-LIME's effectiveness.

        \begin{mycomment}
          We appreciate your sharp observations.
          We additionally conducted qualitative and quantitative comparisons
          between Anchor and R-LIME,
          which demonstrated that R-LIME generates more informative and
          general explanations than Anchor (see \cref{sec:exp-qual,sec:exp-anchor}).
        \end{mycomment}
\end{enumerate}
\section*{Responding to Reviewer \#4}
The authors should kindly explain why there is not a quantitative comparison
between their proposed method R-LIME and Anchor. The lack of the comparison
makes it hard to evaluate the impact of the proposed model.

\begin{mycomment}
  We appreciate your insightful comments.
  We additionally conducted qualitative and quantitative comparisons
  between Anchor and R-LIME,
  which demonstrated that R-LIME generates more informative and
  general explanations than Anchor (see \cref{sec:exp-qual,sec:exp-anchor}).
\end{mycomment}

\section*{Responding to Reviewer \#5}
\begin{itemize}
  \setlength{\itemsep}{15pt}
  \item It would be beneficial to move the comparison of R-LIME with Anchor
        and LIME to the Related Work section for improved clarity and
        organization.

        \begin{mycomment}
          We appreciate your insightful suggestion.
          We interpreted your suggestion to mean that we should move
          \cref{fig:example} and its explanation to \cref{sec:related-work}.
          After discussing the most understandable structure of our paper,
          we concluded that we should present effectiveness of R-LIME
          compared to closely related methods in \cref{sec:introduction},
          before we overview other existing methods in \cref{sec:related-work}.
        \end{mycomment}

  \item The authors should consider exploring a more compatible method than the
        KL-LUCB algorithm to achieve higher accuracy. Although the experimental
        results suggest a minor effect, there may be potential underlying issues
        that need to be addressed.

        \begin{mycomment}
          Thank you for your valuable feedback.
          While our results suggest that the practical effect of using
          the KL-LUCB algorithm is negligible,
          we acknowledge the need to address its theoretical issues.
          Our focus is on presenting our novel framework for local
          interpretability, not the detailed algorithm.
          Thus, we leave the issues for future work due to space constraints.
          However, we deeply appreciate your sharp observations.
        \end{mycomment}

  \item The title of the `Challenges and Future Work' section could be more
        aptly replaced with `Discussion' to better reflect the content.

        \begin{mycomment}
          Thank you for your suggestion. We renamed the section to `Discussion'
          to clearly reflect the content.
        \end{mycomment}
\end{itemize}

\newcommand{\sampleindex}[1]{\ifnum#1=0 \Asample\else\Bsample\fi}
\def\AB#1{\ifnum#1=0 A\else B\fi}

\def\paper{

@@

\section{Introduction}\label{sec:introduction}
In recent years,
complex machine learning models, such as deep neural networks and random forests,
have been widely introduced in various industrial fields
due to their significant improvements in accuracy.
However,
their increasing complexity and black-box nature pose challenges,
particularly in critical decision-making scenarios such as healthcare and finance,
where the lack of transparency becomes a major obstacle to implementation.
In order to address this problem,
extensive research has focused on post-hoc explanations for complex models
~\cite{guidotti2018local,ribeiro2016why,ribeiro2018anchors}.
Post-hoc explanation methods are categorized
into \emph{model-dependent} and \emph{model-agnostic} methods
based on their dependence on the model's structure,
with the latter further classified into \emph{global} and \emph{local} methods
based on the locality in the input space~\cite{samek2021explaining}.
\begin{figure}[tbp]
  \def\scale{0.38}
  \centering
  \begin{subfigure}[t]{0.55\textwidth}
    \centering
    \includegraphics[scale=\scale]{example-instance}
    \caption{Focal point.}\label{fig:example-instance}
    \vspace{0.5cm}
  \end{subfigure}
  \begin{subfigure}[t]{0.45\textwidth}
    \begin{subfigure}[t]{\textwidth}
      \centering
      \includegraphics[scale=\scale]{example-lime}
      \caption{%
        Explanation by LIME\@.
        It provides contributions of each feature to the output,
        but does not explicitly indicate its scope.
      }\label{fig:example-lime}
      \vspace{0.4cm}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
      \centering
      \includegraphics[scale=\scale]{example-anchor}
      \caption{%
        Explanation by Anchor.
        It provides the effective scope of the explanation,
        but does not show the influence of each feature.
      }\label{fig:example-anchor}
    \end{subfigure}
  \end{subfigure}
  \hspace{0.3cm}
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \vspace{-2.24cm}
    \includegraphics[scale=\scale]{example-rlime}
    \caption{%
      Explanation by R-LIME\@.
      It provides both contributions of each feature and
      its effective scope.
    }\label{fig:example-rlime}
  \end{subfigure}
  \caption[Example of explanations by LIME, Anchor and R-LIME]{%
    Example of explanations by LIME~\cite{ribeiro2016why},
    Anchor~\cite{ribeiro2018anchors} and R-LIME (our proposed method)
    for a sentiment prediction model.
  }\label{fig:example}
\end{figure}

@@

\section{Related Work}\label{sec:related-work}
\begin{figure}[tbp]
  \centering
  \def\w{2.5}
  \def\ww{5.0}
  \def\h{0.5}
  \def\hh{1.3}
  \def\hhh{1.8}
  \def\hhhh{2.6}
  \begin{tikzpicture}[scale=0.9,nodestyle/.style={rectangle,auto}]
    \node[nodestyle] (post-hoc) at (0,0){post-hoc};
    \node[nodestyle] (dependent) at (-\w,-\hh){%
      \begin{tabular}{c}
        model-dependent \\
        (DTD~\cite{montavon2017explaining}, LRP~\cite{bach2015pixel})
      \end{tabular}
    };
    \node[nodestyle] (agnostic) at (\w,-\hh){\textbf{model-agnostic}};
    \node[nodestyle] (global) at (0,-\hhhh){%
      \begin{tabular}{c}
        global \\
        (PDP~\cite{friedman2001greedy}, ALE~\cite{apley2020visualizing})
      \end{tabular}
    };
    \node[nodestyle] (local) at (\ww,-\hhhh){%
      \begin{tabular}{c}
        \textbf{local} \\
        (LIME~\cite{ribeiro2016why}, Anchor~\cite{ribeiro2018anchors}, \underline{R-LIME})
      \end{tabular}
    };
    \draw(post-hoc) -- (0,-\h);
    \draw(dependent) -- (-\w,-\h) -- (\w,-\h) -- (agnostic);
    \draw(agnostic) -- (\w,-\hhh);
    \draw(global) -- (0,-\hhh)  -- (\ww,-\hhh) -- (local);
  \end{tikzpicture}
  \caption{%
    Categorization of post-hoc explanation methods.
    We focus on \emph{model-agnostic} and \emph{local} methods,
    which explain model's local behavior using only its output.
  }\label{fig:post-hoc}
\end{figure}
In this section,
we overview existing research on post-hoc explanation methods,
which explain the behavior of black-box models already trained.
As shown in \cref{fig:post-hoc},
post-hoc methods are classified into several categories.

@@

Model-agnostic methods are further categorized into
\emph{global} and \emph{local} methods based on their locality in the input space.
Global methods,
such as partial dependence plots (PDP)~\cite{friedman2001greedy}
and accumulated local effects (ALE)~\cite{apley2020visualizing},
aim to explain the model's behavior across the entire input space.
However, providing global explanations becomes challenging
as the model's complexity increases.
In contrast, local methods,
such as \hl{individual conditional expectation (ICE)}~\cite{goldstein2015peeking},
local interpretable model-agnostic explanations
(LIME)~\cite{ribeiro2016why}, Anchor~\cite{ribeiro2018anchors} and
\hl{shapley additive explanations (SHAP)}~\cite{lundberg2017unified},
explain the model's behavior in the vicinity of a specific input.
While they offer explanations simpler and more accurate than global methods,
the scope of the explanation is limited locally.

@@

\section{Experiments}
To verify the effectiveness of our method,
we conducted qualitative and quantitative comparisons of R-LIME
with LIME and Anchor, using a real-world dataset.
\hl{Our code for R-LIME is available on GitHub}\footnote{\url{https://github.com/g-ohara/rlime}}.

\newpage
\subsection{Qualitative Evaluation}\label{sec:exp-qual}
\subsubsection{Experimental Setup}\label{sec:exp-setting}
{%
  \renewcommand{\arraystretch}{1.05}
  \begin{table}[tbp]
    \centering
    \caption[Attributes of the recidivism dataset used in the experiments]{%
      Attributes of the recidivism dataset used in the experiments.
      Continuous features are all discretized,
      and only binary and ordinal features are considered.
    }\label{tab:rcdv}
    \begin{tabular}{llc}
      \toprule
      Attribute              & Overview                              & \# of Possible Values \\
      \midrule
      Race                   & Race (Black or White)                 & 2                     \\
      Alcohol                & Presence of serious alcohol issues    & 2                     \\
      Junky                  & Drug usage                            & 2                     \\
      Supervised Release     & Supervised release                    & 2                     \\
      Married                & Marital status                        & 2                     \\
      Felony                 & Felony or not                         & 2                     \\
      WorkRelease            & Participation in work release program & 2                     \\
      Crime against Property & Crime against property or not         & 2                     \\
      Crime against Person   & Crime against a person or not         & 2                     \\
      Gender                 & Gender (Female or Male)               & 2                     \\
      Priors                 & Number of prior offenses              & 4                     \\
      YearsSchool            & Years of formal education completed   & 4                     \\
      PrisonViolations       & Number of prison rule violations      & 3                     \\
      Age                    & Age                                   & 4                     \\
      MonthsServed           & Months served in prison               & 4                     \\
      \midrule
      Recidivism             & Recidivism or not                     & 2                     \\
      \bottomrule
    \end{tabular}
  \end{table}
}

@@

    \def\dir{src/experiments/exp1/ver1/examples/output}
    \def\Asample{0012}
    \def\Bsample{0011}

@@

  {%
    \def\scale{0.315}
    \def\dir{exp1/ver1/examples/output}
    \def\imgwidth{0.3\textwidth}
    \def\hspacebase{\hspace{-1.5em}}
    \def\vspacebase{\vspace{0.5em}}
    \def\vspacebeforecaption{\vspace{-0.4em}}
    \begin{figure}[t]
      \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \begin{subfigure}[t]{\textwidth}
          \hspace{-10pt}
          \includegraphics[scale=\scale]{exp1/ver1/examples/output/lime-0012}
          \caption{LIME}\label{fig:lime-0}
          \vspace{1.0em}
        \end{subfigure}

        \vspace{10pt}
        \begin{subfigure}[t]{\textwidth}
          \centering
          \includegraphics[scale=0.33]{exp1/ver2/examples/anchor-0012-70}  % chktex 8
          \caption{\hl{Anchor ($\tau=0.70$)}}\label{fig:anchor-0-70}
          \vspace{1.0em}
        \end{subfigure}

        \vspace{10pt}
        \begin{subfigure}[t]{\textwidth}
          \centering
          \includegraphics[scale=0.33]{exp1/ver2/examples/anchor-0012-90}  % chktex 8
          \caption{\hl{Anchor ($\tau=0.90$)}}
          \vspace{1.0em}
        \end{subfigure}
      \end{subfigure}
      \hfill
      \begin{subfigure}[t]{0.45\textwidth}
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{-5pt}
          \includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-0012-70}  % chktex 8
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.70$)}\label{fig:rlime-0-70}
          \vspacebase{}
        \end{subfigure}
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{-17pt}
          \includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-0012-90}  % chktex 8
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.90$)}
          \vspacebase{}
        \end{subfigure}
      \end{subfigure}
      \caption[Explanation for Instance A by LIME and R-LIME]{%
        Explanation for Instance A by LIME and R-LIME\@.
      }\label{fig:A}
    \end{figure}
    \begin{figure}[t]
      \begin{subfigure}[t]{0.45\textwidth}
        \begin{subfigure}[t]{\textwidth}
          \hspace{-26.5pt}
          \includegraphics[scale=\scale]{exp1/ver1/examples/output/lime-0011}
          \caption{LIME}\label{fig:lime-1}
          \vspace{1.0em}
        \end{subfigure}

        \vspace{10pt}
        \begin{subfigure}[t]{\textwidth}
          \centering
          \includegraphics[scale=0.33]{exp1/ver2/examples/anchor-0011-70}  % chktex 8
          \caption{\hl{Anchor ($\tau=0.70$)}}
          \vspace{1.0em}
        \end{subfigure}

        \vspace{10pt}
        \begin{subfigure}[t]{\textwidth}
          \centering
          \includegraphics[scale=0.33]{exp1/ver2/examples/anchor-0011-90}  % chktex 8
          \caption{\hl{Anchor ($\tau=0.90$)}}
          \vspace{1.0em}
        \end{subfigure}
      \end{subfigure}
      \hfill
      \begin{subfigure}[t]{0.45\textwidth}
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{-5pt}
          \includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-0011-70}  % chktex 8
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.90$)}
          \vspacebase{}
        \end{subfigure}
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{-20pt}
          \includegraphics[scale=\scale]{exp1/ver1/examples/output/newlime-0011-90}  % chktex 8
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.90$)}\label{fig:rlime-1-90}
          \vspacebase{}
        \end{subfigure}
      \end{subfigure}
      \caption[Explanation for Instance B by LIME and R-LIME]{%
        Explanation for Instance B by LIME and R-LIME\@.
      }\label{fig:B}
    \end{figure}
  }

@@

\hl{%
  Anchor provides conditions for the model's output to be fixed with high
  probability.
  For example,
  the explanation for instance A under $\tau=0.70$
} (\cref{fig:anchor-0-70})
\hl{%
  means that the model will predict with 75.66 \% probability
  that the prisoner will commit no more crimes
  when a prisoner is older than 33 and has one prior offense.
  Although it clearly provides the explanation's application scope,
  it does not provide details about how these conditions affect the model's output.
}

@@

\begin{figure}[t]
  \begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[scale=0.36,valign=t]{exp2/box_plot}
    \caption[Comparison of Local Accuracy between R-LIME and LIME]{%
      Comparison of local accuracy between LIME and R-LIME\@.
      R-LIME achieved higher and less variable accuracy compared to LIME\@.
    }\label{fig:box-plot}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[scale=0.35,valign=t]{exp2b/comp_cov}
    \vspace{3pt}
    \caption[Comparison of Coverage between Anchor and R-LIME]{%
      \hl{%
        Comparison of coverage between Anchor and R-LIME\@.
        R-LIME achieved higher coverage compared to Anchor
        for almost values of $\tau$, especially for relatively small $\tau$.
      }
    }\label{fig:coverage}
  \end{subfigure}
  \caption{Comparison of existing methods (LIME, Anchor) and R-LIME.}
\end{figure}

@@

\subsection{\hl{Quantitative Evaluation: Anchor vs. R-LIME}}\label{sec:exp-anchor}
\subsubsection{\hl{Experimental Setup}}
\hl{%
  To demonstrate that R-LIME explanations are more general than Anchor,
  we conducted a comparison of the coverage of explanations
  between Anchor and R-LIME\@.
  Under the same settings as in
}\cref{sec:exp-setting},
\hl{%
  we generated Anchor and R-LIME explanations
  for 704 instances from the test data of the recidivism dataset,
  under the values of $\tau=0.65,0.70,0.75,0.80,0.85,0.90$.
}

\subsubsection{\hl{Experimental Results}}
\hl{The results are presented in} \cref{fig:coverage},
\hl{%
  showing the coverage of the explanations by Anchor and R-LIME\@.
  The coverage of explanations generated by R-LIME is higher compared to Anchor
  for almost values of $\tau$, especially for relatively small $\tau$.
  It is because of the flexibility of the linear approximation models learned by
  R-LIME, which captures the decision boundary more precisely.
  In contrast,
  Anchor uses only the intervals of each feature discretized in advance,
  which cannot capture the decision boundary flexibly and makes its scope narrow.
}

>>>>

\usepackage[export]{adjustbox} % for valign option in \includegraphics
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amssymb} % for \mathbb
\usepackage{array} % for m column type
% \usepackage{bbm} % for \mathbbm
\usepackage{dsfont}
\newcommand{\mathbbm}[1]{\mathds{#1}}
\usepackage{booktabs} % for \toprule, \midrule, \bottomrule
\usepackage{cleveref} % for \cref
\usepackage{csvsimple} % for \csvreader
\usepackage[T1]{fontenc} % for T1 font encoding
\usepackage{graphicx} % for \includegraphics
\usepackage{pgffor} % for \foreach
\usepackage[labelformat=simple]{subcaption} % for subfigure environment
\usepackage{tikz}
\usetikzlibrary{positioning}

@@

\begin{document}
\newcommand{\sampleindex}[1]{\ifnum#1=0 \Asample\else\Bsample\fi}
\def\AB#1{\ifnum#1=0 A\else B\fi}

@@

\section{Introduction}
In recent years,
complex machine learning models, such as deep neural networks and random forests,
have been widely introduced in various industrial fields
due to their significant improvements in accuracy.
However,
their increasing complexity and black-box nature pose challenges,
particularly in critical decision-making scenarios such as healthcare and finance,
where the lack of transparency becomes a major obstacle to implementation.
In order to address this problem,
extensive research has focused on post-hoc explanations for complex models
~\cite{guidotti2018local,ribeiro2016why,ribeiro2018anchors}.
Post-hoc explanation methods are categorized
into \emph{model-dependent} and \emph{model-agnostic} methods
based on their dependence on the model's structure,
with the latter further classified into \emph{global} and \emph{local} methods
based on the locality in the input space~\cite{samek2021explaining}.
\begin{figure}[tbp]
  \def\scale{0.38}
  \centering
  \begin{subfigure}[t]{0.55\textwidth}
    \centering
    \includegraphics[scale=\scale]{example-instance}
    \caption{Focal point.}\label{fig:example-instance}
    \vspace{0.5cm}
  \end{subfigure}
  \begin{subfigure}[t]{0.45\textwidth}
    \begin{subfigure}[t]{\textwidth}
      \centering
      \includegraphics[scale=\scale]{example-lime}
      \caption{%
        Explanation by LIME\@.
        It provides contributions of each feature to the output,
        but does not explicitly indicate its scope.
      }\label{fig:example-lime}
      \vspace{0.4cm}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
      \centering
      \includegraphics[scale=\scale]{example-anchor}
      \caption{%
        Explanation by Anchor.
        It provides the effective scope of the explanation,
        but does not show the influence of each feature.
      }\label{fig:example-anchor}
    \end{subfigure}
  \end{subfigure}
  \hspace{0.3cm}
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \vspace{-2.24cm}
    \includegraphics[scale=\scale]{example-rlime}
    \caption{%
      Explanation by R-LIME\@.
      It provides both contributions of each feature and
      its effective scope.
    }\label{fig:example-rlime}
  \end{subfigure}
  \caption[Example of explanations by LIME, Anchor and R-LIME]{%
    Example of explanations by LIME~\cite{ribeiro2016why},
    Anchor~\cite{ribeiro2018anchors} and R-LIME (our proposed method)
    for a sentiment prediction model.
  }\label{fig:example}
\end{figure}

@@

\section{Related Work}
\begin{figure}[tbp]
  \centering
  \def\w{2.5}
  \def\ww{5.0}
  \def\h{0.5}
  \def\hh{1.3}
  \def\hhh{1.8}
  \def\hhhh{2.6}
  \begin{tikzpicture}[scale=0.9,nodestyle/.style={rectangle,auto}]
    \node[nodestyle] (post-hoc) at (0,0){post-hoc};
    \node[nodestyle] (dependent) at (-\w,-\hh){%
      \begin{tabular}{c}
        model-dependent \\
        (DTD~\cite{montavon2017explaining}, LRP~\cite{bach2015pixel})
      \end{tabular}
    };
    \node[nodestyle] (agnostic) at (\w,-\hh){\textbf{model-agnostic}};
    \node[nodestyle] (global) at (0,-\hhhh){%
      \begin{tabular}{c}
        global \\
        (PDP~\cite{friedman2001greedy}, ALE~\cite{apley2020visualizing})
      \end{tabular}
    };
    \node[nodestyle] (local) at (\ww,-\hhhh){%
      \begin{tabular}{c}
        \textbf{local} \\
        (LIME~\cite{ribeiro2016why}, Anchor~\cite{ribeiro2018anchors}, \underline{R-LIME})
      \end{tabular}
    };
    \draw(post-hoc) -- (0,-\h);
    \draw(dependent) -- (-\w,-\h) -- (\w,-\h) -- (agnostic);
    \draw(agnostic) -- (\w,-\hhh);
    \draw(global) -- (0,-\hhh)  -- (\ww,-\hhh) -- (local);
  \end{tikzpicture}
  \caption{%
    Categorization of post-hoc explanation methods.
    We focus on \emph{model-agnostic} and \emph{local} methods,
    which explain model's local behavior using only its output.
  }\label{fig:post-hoc}
\end{figure}
In this section,
we overview existing research on post-hoc explanation methods,
which explain the behavior of black-box models already trained.
As shown in \cref{fig:post-hoc},
post-hoc methods are classified into several categories.

@@

Model-agnostic methods are further categorized into
\emph{global} and \emph{local} methods based on their locality in the input space.
Global methods,
such as partial dependence plots (PDP)~\cite{friedman2001greedy}
and accumulated local effects (ALE)~\cite{apley2020visualizing},
aim to explain the model's behavior across the entire input space.
However, providing global explanations becomes challenging
as the model's complexity increases.
In contrast, local methods,
such as individual conditional expectation (ICE)~\cite{goldstein2015peeking},
local interpretable model-agnostic explanations
(LIME)~\cite{ribeiro2016why}, Anchor~\cite{ribeiro2018anchors} and
shapley additive explanations (SHAP)~\cite{lundberg2017unified},
explain the model's behavior in the vicinity of a specific input.
While they offer explanations simpler and more accurate than global methods,
the scope of the explanation is limited locally.

@@

\section{Experiments}
To verify the effectiveness of our method,
we conducted qualitative and quantitative comparisons of R-LIME
with LIME and Anchor, using a real-world dataset.
Our code for R-LIME is available on GitHub\footnote{\url{https://github.com/g-ohara/rlime}}.

\newpage
\subsection{Qualitative Evaluation}
\subsubsection{Experimental Setup}\label{sec:exp-setting}
{%
  \renewcommand{\arraystretch}{1.05}
  \begin{table}[tbp]
    \centering
    \caption[Attributes of the recidivism dataset used in the experiments]{%
      Attributes of the recidivism dataset used in the experiments.
      Continuous features are all discretized,
      and only binary and ordinal features are considered.
    }\label{tab:rcdv}
    \begin{tabular}{llc}
      \toprule
      Attribute              & Overview                              & \# of Possible Values \\
      \midrule
      Race                   & Race (Black or White)                 & 2                     \\
      Alcohol                & Presence of serious alcohol issues    & 2                     \\
      Junky                  & Drug usage                            & 2                     \\
      Supervised Release     & Supervised release                    & 2                     \\
      Married                & Marital status                        & 2                     \\
      Felony                 & Felony or not                         & 2                     \\
      WorkRelease            & Participation in work release program & 2                     \\
      Crime against Property & Crime against property or not         & 2                     \\
      Crime against Person   & Crime against a person or not         & 2                     \\
      Gender                 & Gender (Female or Male)               & 2                     \\
      Priors                 & Number of prior offenses              & 4                     \\
      YearsSchool            & Years of formal education completed   & 4                     \\
      PrisonViolations       & Number of prison rule violations      & 3                     \\
      Age                    & Age                                   & 4                     \\
      MonthsServed           & Months served in prison               & 4                     \\
      \midrule
      Recidivism             & Recidivism or not                     & 2                     \\
      \bottomrule
    \end{tabular}
  \end{table}
}

@@

    \def\dir{src/experiments/exp1/}
    \def\Asample{0012}
    \def\Bsample{0011}

@@

  {%
    \def\scale{0.315}
    \def\dir{exp1/}
    \def\imgwidth{0.3\textwidth}
    \def\hspacebase{\hspace{-1.5em}}
    \def\vspacebase{\vspace{0.5em}}
    \def\vspacebeforecaption{\vspace{-0.4em}}
    \begin{figure}[t]
      \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \begin{subfigure}[t]{\textwidth}
          \hspace{-10pt}
          \includegraphics[scale=\scale]{exp1/lime-0012}
          \caption{LIME}\label{fig:lime-0}
          \vspace{1.0em}
        \end{subfigure}

        \vspace{10pt}
        \begin{subfigure}[t]{\textwidth}
          \centering
          \includegraphics[scale=0.33]{exp1/anchor-0012-70}  % chktex 8
          \caption{Anchor ($\tau=0.70$)}\label{fig:anchor-0-70}
          \vspace{1.0em}
        \end{subfigure}

        \vspace{10pt}
        \begin{subfigure}[t]{\textwidth}
          \centering
          \includegraphics[scale=0.33]{exp1/anchor-0012-90}  % chktex 8
          \caption{Anchor ($\tau=0.90$)}
          \vspace{1.0em}
        \end{subfigure}
      \end{subfigure}
      \hfill
      \begin{subfigure}[t]{0.45\textwidth}
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{-5pt}
          \includegraphics[scale=\scale]{exp1/rlime-0012-70}  % chktex 8
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.70$)}\label{fig:rlime-0-70}
          \vspacebase{}
        \end{subfigure}
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{-17pt}
          \includegraphics[scale=\scale]{exp1/rlime-0012-90}  % chktex 8
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.90$)}
          \vspacebase{}
        \end{subfigure}
      \end{subfigure}
      \caption[Explanation for Instance A by LIME and R-LIME]{%
        Explanation for Instance A by LIME and R-LIME\@.
      }\label{fig:A}
    \end{figure}
    \begin{figure}[t]
      \begin{subfigure}[t]{0.45\textwidth}
        \begin{subfigure}[t]{\textwidth}
          \hspace{-26.5pt}
          \includegraphics[scale=\scale]{exp1/lime-0011}
          \caption{LIME}\label{fig:lime-1}
          \vspace{1.0em}
        \end{subfigure}

        \vspace{10pt}
        \begin{subfigure}[t]{\textwidth}
          \centering
          \includegraphics[scale=0.33]{exp1/anchor-0011-70}  % chktex 8
          \caption{Anchor ($\tau=0.70$)}
          \vspace{1.0em}
        \end{subfigure}

        \vspace{10pt}
        \begin{subfigure}[t]{\textwidth}
          \centering
          \includegraphics[scale=0.33]{exp1/anchor-0011-90}  % chktex 8
          \caption{Anchor ($\tau=0.90$)}
          \vspace{1.0em}
        \end{subfigure}
      \end{subfigure}
      \hfill
      \begin{subfigure}[t]{0.45\textwidth}
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{-5pt}
          \includegraphics[scale=\scale]{exp1/rlime-0011-70}  % chktex 8
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.90$)}
          \vspacebase{}
        \end{subfigure}
        \begin{subfigure}[t]{\textwidth}
          \hspacebase{}
          \hspace{-20pt}
          \includegraphics[scale=\scale]{exp1/rlime-0011-90}  % chktex 8
          \vspacebeforecaption{}
          \caption{R-LIME ($\tau=0.90$)}\label{fig:rlime-1-90}
          \vspacebase{}
        \end{subfigure}
      \end{subfigure}
      \caption[Explanation for Instance B by LIME and R-LIME]{%
        Explanation for Instance B by LIME and R-LIME\@.
      }\label{fig:B}
    \end{figure}
  }

@@

Anchor provides conditions for the model's output to be fixed with high
probability.
For example,
the explanation for instance A under $\tau=0.70$
(\cref{fig:anchor-0-70})
means that the model will predict with 75.66 \% probability
that the prisoner will commit no more crimes
when a prisoner is older than 33 and has one prior offense.
Although it clearly provides the explanation's application scope,
it does not provide details about how these conditions affect the model's output.

@@

\begin{figure}[t]
  \begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[scale=0.36,valign=t]{exp2/box_plot}
    \caption[Comparison of Local Accuracy between R-LIME and LIME]{%
      Comparison of local accuracy between LIME and R-LIME\@.
      R-LIME achieved higher and less variable accuracy compared to LIME\@.
    }\label{fig:box-plot}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.48\textwidth}
    \centering
    \includegraphics[scale=0.35,valign=t]{exp2/comp_cov}
    \vspace{3pt}
    \caption[Comparison of Coverage between Anchor and R-LIME]{%
      Comparison of coverage between Anchor and R-LIME\@.
      R-LIME achieved higher coverage compared to Anchor
      for almost values of $\tau$, especially for relatively small $\tau$.
    }\label{fig:coverage}
  \end{subfigure}
  \caption{Comparison of existing methods (LIME, Anchor) and R-LIME.}
\end{figure}

@@

\subsection{Quantitative Evaluation: Anchor vs. R-LIME}
\subsubsection{Experimental Setup}
To demonstrate that R-LIME explanations are more general than Anchor,
we conducted a comparison of the coverage of explanations
between Anchor and R-LIME\@.
Under the same settings as in
\cref{sec:exp-setting},
we generated Anchor and R-LIME explanations
for 704 instances from the test data of the recidivism dataset,
under the values of $\tau=0.65,0.70,0.75,0.80,0.85,0.90$.

\subsubsection{Experimental Results}
The results are presented in \cref{fig:coverage},
showing the coverage of the explanations by Anchor and R-LIME\@.
The coverage of explanations generated by R-LIME is higher compared to Anchor
for almost values of $\tau$, especially for relatively small $\tau$.
It is because of the flexibility of the linear approximation models learned by
R-LIME, which captures the decision boundary more precisely.
In contrast,
Anchor uses only the intervals of each feature discretized in advance,
which cannot capture the decision boundary flexibly and makes its scope narrow.

\section{Discussion}
 {%
  \def\imgwidth{0.47\textwidth}
  \begin{figure}[t]
    \centering
    \begin{subfigure}[t]{\imgwidth}
      \centering
      \includegraphics[width=0.7\textwidth]{visual-rlime3}
      \caption{R-LIME for balanced label distribution.}
    \end{subfigure}
    \begin{subfigure}[t]{\imgwidth}
      \centering
      \includegraphics[width=0.7\textwidth]{visual-rlime-imbalanced}
      \caption{R-LIME for imbalanced label distribution.
      }
    \end{subfigure}
    \caption[Behavior of R-LIME for balanced and imbalanced label distribution]{%
      Behavior of R-LIME for balanced and imbalanced label distribution.
      In case of imbalanced label distribution,
      the approximation region covers the entire input space and the
      linear approximation model always outputs the majority label.
    }\label{fig:imbalanced}
  \end{figure}
 }
